---
title: "fars_details"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
library(maps)
```

# Package Description
`fars` package reads and plots Fatality Analysis Reporting System (FARS) data from the [National Highway Traffic Safety Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is a nationwide census, providing the American public yearly data, regarding fatal injuries suffered in motor vehicle traffic crashes.


## Included data
Data files included within the package are:
```{r}

list.files(system.file("extdata", package = "fars"))

```


## Package Functions

### Function `make_filename`
This function returns file name and path to the data files:
```{r}
make_filename(2014)
```


### Function `fars_read_years`
Ancillary function used by `fars_summarize_years`
```{r}

fars_read_years(2014)

```


### Function `fars_summarize_years`
This function summarizes yearly accidents data, by month.
```{r}
plot(fars_summarize_years(2013))
fars_summarize_years(c(2015, 2013))
```


### Function `fars_map_state`
The function displays a state map plot including accidents location by year
```{r}
state_num <- 26 # Michigan
yr <- 2013
fars_map_state(state_num, yr)
```
